---
title: "PSY 8712 Week 8 Project"
author: "Patrick McGonagle"
date: "2026-03-20"
output: html_document
---

# Reproducible Image and Online Resources

```{r}

```

# Script Settings and Resources 
```{r, message = FALSE, warning = FALSE}
setwd(dirname(rstudioapi::getActiveDocumentContext()$path)) # Working Directory 
library(tidyverse)
library(knitr)
```

# Data Import and Cleaning 

This is where the data was imported and cleaned. Time variables were coerced into Posix, factor variables were re-coded according codebook, question 5 was reverse coded, new variables were created for subsequent visualization.
```{r, message = FALSE}
week8_tbl <- read_csv("../data/week3.csv") |>
  mutate(timeStart = ymd_hms(timeStart), 
         timeEnd = ymd_hms(timeEnd),
         condition = fct_recode(condition,"Block A" = "A", "Block B" = "B","Control" = "C"),
         gender = fct_recode(gender, "Male" = "M", "Female" = "F"), 
         q5 = 6 - q5, 
         m_q1_q6 = rowMeans(pick(q1:q6), na.rm = TRUE),
         m_q8_q10 = rowMeans(pick(q8:q10), na.rm = TRUE))
```

# Visualization 

Data for the first six responses is shown and the mean scores of Q8–Q10 were regressed on the mean scores of Q1–Q6.
```{r, echo = FALSE, warning = FALSE, message = FALSE}
week8_tbl |>
  select(q1:q6) |>
  kable(caption = "Responses for Questions 1 through 6")
week8_tbl |>
  ggplot(aes(x = m_q1_q6, y = m_q8_q10)) +
  geom_jitter(width = 0.2, height = 0.2) +
  geom_smooth(method = "lm", color = "purple", se = TRUE) +
  labs(title = "Relationship Between Mean Scores of Q1-Q6 and Q8-Q10",
       x = "Means of Questions 1-6",
       y = "Means of Questions 8-10")
```

# Analysis

In this code, a pearson correlation test is run on the previously visualized variables. Afterwards, a reproducible paragraph is generated and can be augmented by new values. 
```{r}
# Correlation test between mean scores
cor <- week8_tbl |>
  cor.test(formula = ~ m_q1_q6 + m_q8_q10, data = _)

# Correlation value 
cor_val <- cor$estimate

# P value 
p_val <- cor$p.value
```

After running a Pearson correlation test on the mean scores of Q1-Q6 and Q8-Q10, a correlation was estimated at `r sub("^(-?)0\\.", "\\1.", sprintf("%.2f", cor_val))` with a p-value of `r sub("^(-?)0\\.", "\\1.", sprintf("%.3f", p_val))`. This p-value indicates that the probability of observing this correlation by random chance is exceptionally high and thus, the null hypothesis is not rejected and the evidence points to a non-statistically significant relationship between these values. 

# Data Export

```{r}

```
